---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# slrplotfun

<!-- badges: start -->
[![R-CMD-check](https://github.com/registercentrum/rcplot/workflows/R-CMD-check/badge.svg)](https://github.com/registercentrum/rcplot/actions)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of slrplotfun is to implement the design used by the Swedish Arthroplasty Register with figures produced by ggplot2. Functions are used for the annual report and more.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("registercentrum/rcplot")
```
## Example

Here are some example plots but please see the individual manual pages for a comprehensive list.

```{r example}
library(rcplot)
set.seed(123)

# Create some data
df <- data.frame(
  age = rpois(100000, 65),
  gender = sample(c('Woman', 'Woman', 'Man'), size = 100000, replace = TRUE))

# Age pyramid
age_pyramid(df, age_var = 'age', fill_var = 'gender',
            man_level = 'Man', title = "This is an age pyramid")

# Bar plot
bar_plot(df = ggplot2::diamonds, x_var = 'color',
         fill_var = 'cut', y_breaks = 2)

# KM-plot with 2 levels
survfit_obj <- survival::survfit(
  survival::Surv(time/365.24, status) ~ sex,
  data = survival::colon
)

km_plot(survfit_obj, y_lim = c(0,100), y_breaks = 10, x_lim = c(0,9))

# Line plot
line_plot(df = ggplot2::diamonds, x_var = 'cut', color_var = 'color', y_breaks = 2)

# Map figure of Counties, Sweden
region_coords <- rcplot::counties
region_coords[["var"]] <- factor(
  sample(c("Sämst", "Dålig", "Bra", "Bäst"),
         size = nrow(region_coords), replace = TRUE),
  ordered = TRUE,
  levels = c("Sämst", "Dålig", "Bra", "Bäst")
)

map_plot(
  df = region_coords,
  fill_var = "var",
  fill_colors = rc_colors(n = 4, type = "RYG")
)

# Map figure of Västra Götalandsregionen
vgregion <- dplyr::filter(rcplot::municipalities, RegionID == "14")

vgregion[["var"]] <- factor(
  sample(c("Sämst", "Dålig", "Bra", "Bäst"),
         size = nrow(vgregion), replace = TRUE),
  ordered = TRUE,
  levels = c("Sämst", "Dålig", "Bra", "Bäst")
)

map_plot(
  df = vgregion,
  fill_var = "var",
  fill_colors = rc_colors(n = 4, type = "RYG")
)
```

